# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
Data comes from a personal activity monitoring device.
This device collects data at 5 minute intervals through out the day. The data
consists of two months of data from an anonymous individual collected during
the months of October and November, 2012 and include the number of steps
taken in 5 minute intervals each day.
The dataset is stored in a comma-separated-value (CSV) file and there are a
total of 17,568 observations in this dataset.

```{r}
# unzip and load activity.zip dataset
#Download and unzip files
destFile = "activity.csv"
if(!file.exists(destFile)) {
    unzip("activity.zip", exdir=".")
}
activity <- read.csv (destFile)

head (activity)
```

The variables included in this dataset are:

* **steps:** Number of steps taking in a 5-minute interval (missing values are
coded as NA)

* **date:** The date on which the measurement was taken in YYYY-MM-DD
format

* **interval:** Identifier for the 5-minute interval in which measurement was
taken

## What is mean total number of steps taken per day?
```{r}
stepsForDays <- aggregate(activity$steps, by=list(activity$date), FUN="sum")
hist (stepsForDays$x, main = "Histogram of Steps For Days", xlab ="Steps For Days")
m1 <- mean(stepsForDays$x,na.rm = TRUE)
m2 <- median(stepsForDays$x,na.rm = TRUE)
```

**Mean** total number of steps taken per day:  `r as.integer(m1)` 

**Median** total number of steps taken per day: `r as.integer(m2)` 

## What is the average daily activity pattern?
```{r}

```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
